Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-06-05 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded the appropriate CDSRs that could be represented by our approach. For the classrooms these were the front and back, and the front and back rows of desk. For the studios these were the kitchen, office and living areas. These manually encoded regions were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

We consider a \textit{problem instance} to be a room and a sought CDSR type. For each room for which we have a human-labelled target region of the sought type, we generate an \textit{inferred region} using analogical transfer. To assess the quality of the transfer, we calculate precision ($p$, the proportion of the inferred region that overlaps with the target region) and recall ($r$, the proportion of the target region that overlaps with the inferred region) as follows:

\begin{equation}
	p=\frac{area(inferred\ region \cap target\ region)}{area(inferred\ region)}
\end{equation}
\begin{equation}
	r=\frac{area(inferred\ region \cap target\ region)}{area(target\ region)}
\end{equation}

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the manually annotated CDSR in the target and appropriate target region; and the region for the whole room and the target region. 
 Results comparing transferred and target regions measure how well the output of our system matches user expectations. Results comparing the manual annotations to the target regions measure how well the anchor point-based regions we chose match the users' regions (who were not constrained to anchor points). Results comparing whole rooms to target regions provide a baseline performance for comparison.

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.47 $\sigma$=.37, $\bar{r}$=.46 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.30, $\bar{r}$=.67 $\sigma$=.25 & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

@@

To assess overall performance, Table~\ref{tab:overall} summarizes the results across all problem instances against user-defined target regions from three different users. The inferred regions achieved a precision of .47 ($\sigma$=.37) and a recall of .46 ($\sigma$=.38). Comparing the manually encoded regions against each target region results in a mean precision of .71 ($\sigma$=.30) and recall of .67 ($\sigma$=.25). The region defined by the room corresponds to the target region with a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.32 $\sigma$=.33, $\bar{r}$=.49 $\sigma$=.41 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.83 $\sigma$=.19  & $\bar{p}$=.16 $\sigma$=.10, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.44 $\sigma$=.37, $\bar{r}$=.56 $\sigma$=.41 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.76 $\sigma$=.27, $\bar{r}$=.28 $\sigma$=.21 & $\bar{p}$=.83 $\sigma$=.31, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.72 $\sigma$=.30, $\bar{r}$=.42 $\sigma$=.26 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.60 $\sigma$=.05, $\bar{r}$=.59 $\sigma$=.34 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.00 $\sigma$=.00, $\bar{r}$=.00 $\sigma$=.00 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.94 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=.40 $\sigma$=.39, $\bar{r}$=.01 $\sigma$=.01 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

>>>>

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded appropriate CDSRs that could be represented by our approach. For the classrooms these were the front and back, and the front and back rows of desks. For the studios these were the kitchen, office and living areas. These manually encoded regions were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

To determine how people define CDSRs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage on which each user was presented with an image of the real room plus an image of the map data generated by the robot onto which the drawing could be done. The webpage\footnote{http://home.csumb.edu/k/katherinelockwood/world/} is shown in the inset in Figure~\ref{fig:ug40}. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

We consider a \textit{problem instance} to be a room and a sought CDSR type. For each room containing a manually encoded CDSR of the sought type, we generate a \textit{transferred region} using analogical transfer. To assess the quality of the transfer, we calculate precision ($p$, the proportion of the transferred region that overlaps with the target region) and recall ($r$, the proportion of the target region that overlaps with the transferred region) as follows:

\begin{equation}
	p=\frac{area(transferred\ region \cap target\ region)}{area(transferred\ region)}
\end{equation}
\begin{equation}
	r=\frac{area(transferred\ region \cap target\ region)}{area(target\ region)}
\end{equation}

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the CDSR we manually encoded for the target room and target region; and the region for the whole room and the target region. 
Results comparing transferred and target regions measure how well our system is able apply a single example to new situations. The comparisons between the manual annotations to the target regions measure how well the anchor points we chose capture the users' regions (who were not constrained to anchor points). Results from the whole room regions provide a baseline performance for comparison.

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Transferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.47 $\sigma$=.37, $\bar{r}$=.46 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.30, $\bar{r}$=.67 $\sigma$=.25 & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance Compared Against Target Regions Defined by Three Users}
  \label{tab:overall}

@@

To assess overall performance, Table~\ref{tab:overall} summarizes the results across all problem instances against user-defined target regions from three different users. The transferred regions achieved a precision of .47 ($\sigma$=.37) and a recall of .46 ($\sigma$=.38). Comparing the manually encoded regions against each target region results in a mean precision of .71 ($\sigma$=.30) and recall of .67 ($\sigma$=.25). The region defined by the room corresponds to the target region with a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.32 $\sigma$=.33, $\bar{r}$=.49 $\sigma$=.41 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.83 $\sigma$=.19  & $\bar{p}$=.16 $\sigma$=.10, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.44 $\sigma$=.37, $\bar{r}$=.56 $\sigma$=.41 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.76 $\sigma$=.27, $\bar{r}$=.28 $\sigma$=.21 & $\bar{p}$=.83 $\sigma$=.31, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.72 $\sigma$=.30, $\bar{r}$=.42 $\sigma$=.26 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.60 $\sigma$=.05, $\bar{r}$=.59 $\sigma$=.34 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.00 $\sigma$=.00, $\bar{r}$=.00 $\sigma$=.00 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.94 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=.40 $\sigma$=.39, $\bar{r}$=.01 $\sigma$=.01 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}
